\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-10-29 paper/mswp2012-proposal.tex
Added another organization example and students

\author{
{\em 188.407: Management von Software Projekten} \vspace{1cm} \\
Group: 12\bigskip \\
Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
Dominik Oberhumer \\ {\small 1025454, 033 534, \href{mailto:e1025454@student.tuwien.ac.at}{e1025454@student.tuwien.ac.at}}\\
$<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author4$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author4@tuwien.ac.at}{author1@tuwien.ac.at}}\\ 
\vspace{4cm}
}

@@

Possible Partners are:
\begin{itemize}
	\item Phase 1:
		\begin{itemize}
			\item Supermarkets
			\item Fitness-Centers
			\item Restaurants
		\end{itemize}
	\item Phase 2 - $"$Embedding to existing services$"$:
		\begin{itemize}
			\item Sport-Community with Tracking (Runtastic, RunKeeper, etc.)
			\item other Sporttracking-Services (Pedometer, etc.)
		\end{itemize}
	\item Phase 3 - $"$Health Organisations$"$:
		\begin{itemize}
			\item Insurances 
		\end{itemize}
\end{itemize}

>>>>

\author{
{\em 188.407: Management von Software Projekten} \vspace{1cm} \\
Group: 12\bigskip \\
Dominik Oberhumer \\ {\small 1025454, 033 534, \href{mailto:e1025454@student.tuwien.ac.at}{e1025454@student.tuwien.ac.at}}\\
Gerhard Schraml \\ {\small 0728067, 033 534, \href{mailto:e0728067@student.tuwien.ac.at}{e0728067@student.tuwien.ac.at}}\\
Johannes Kurz \\ {\small 0727957, 033534, \href{mailto:e0727957@student.tuwien.ac.at}{e0727957@student.tuwien.ac.at}}\\
Matthias Tretter \\ {\small 0726390, 066 937,  \href{mailto:e0726390@student.tuwien.ac.at}{e0726390@student.tuwien.ac.at}}\\
Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\

\vspace{4cm}
}

@@

Possible Partners are:
\begin{itemize}
	\item Phase 1:
		\begin{itemize}
			\item Supermarkets
			\item Fitness-Centers
			\item Restaurants
		\end{itemize}
	\item Phase 2 - $"$Embedding to existing services$"$:
		\begin{itemize}
			\item Sport-Community with Tracking (Runtastic, RunKeeper, etc.)
			\item other Sporttracking-Services (Pedometer, etc.)
		\end{itemize}
	\item Phase 3 - $"$Health Organisations$"$:
		\begin{itemize}
			\item Insurances 
			\item WHO
		\end{itemize}
\end{itemize}
